---
title: "1_clean"
author: "Thomas E. Metherell"
date: "16/08/2021"
output: 
  html_document: 
    keep_md: yes
---

This script cleans data from the Understanding Society dataset for use in our study of digital exclusion and adolescent mental health during the COVID-19 pandemic in the United Kingdom.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Dependencies
We start by loading the necessary dependencies.

```{r dependencies, warning=FALSE}
# Loading dependencies
library(tidyverse)
library(magrittr)
library(scales)
```

# Loading the data
We can now load the data downloaded from the UK Data Service in accordance with the datasets specified in the analysis plan. Here we are using the tab-delimited format; SPSS and Stata equivalents are also available.

```{r load_data}
# Loading youth and individual response datasets from UKHLS waves 9 and 10
W9_raw <- read.delim("Data/Raw/Main_survey/UKDA-6614-tab/tab/ukhls_w9/i_indresp.tab", quote = "")
W9Y_raw <- read.delim("Data/Raw/Main_survey/UKDA-6614-tab/tab/ukhls_w9/i_youth.tab", quote = "")
W10_raw <- read.delim("Data/Raw/Main_survey/UKDA-6614-tab/tab/ukhls_w10/j_indresp.tab", quote = "")
W10Y_raw <- read.delim("Data/Raw/Main_survey/UKDA-6614-tab/tab/ukhls_w10/j_youth.tab", quote = "")

# Loading UKHLS wave 9 household survey dataset
W9hh_raw <- read.delim("Data/Raw/Main_survey/UKDA-6614-tab/tab/ukhls_w9/i_hhresp.tab", quote= "")

# Loading all COVID-19 individual response web survey datasets
for(i in 1:8){
  assign(paste0("CV", i, "w_raw"), read.delim(paste0("Data/Raw/COVID-19/UKDA-8644-tab/tab/c", letters[i], "_indresp_w.tab"), quote = ""))
}

# Loading COVID-19 individual response telephone survey dataset from waves 2 and 6
  CV2t_raw <- read.delim("Data/Raw/COVID-19/UKDA-8644-tab/tab/cb_indresp_t.tab", quote = "")
  CV6t_raw <- read.delim("Data/Raw/COVID-19/UKDA-8644-tab/tab/cf_indresp_t.tab", quote = "")

# Loading COVID-19 youth datasets from waves 4, 6 and 8
for(i in c(4, 6, 8)){
  assign(paste0("CV", i, "Y_raw"), read.delim(paste0("Data/Raw/COVID-19/UKDA-8644-tab/tab/c", letters[i], "_youth_p.tab"), quote = ""))
}
```

# Cleaning the data
We specify a function, `clean_data`, to define negative numbers in the datasets as NAs and select the variables of interest as outlined in the pre-registration documentation.

```{r clean_data}
#######
# Function: clean_data
# Input: a raw data frame
# Method: the function defines any negative numbers as NAs and selects variables of interest in the current study
# Output: a cleaned data frame
#######

clean_data <- function(dataset){
  is.na(dataset[,]) <- dataset[,] < 0
  
  dataset %<>%
    dplyr::select(
      contains("pidp"), # Participant ID
      contains("hidp"), # Household ID
      contains("ageon20200815"), # Participant age
      contains("chsex"), # Sex
      contains("ypsdqtd_dv"), # SDQ Total Difficulties scores
      contains("ypschlth"), # Digital inclusion variables
      contains("fihhmnnet1_dv"),
      contains("hhincome_amount") & !contains("ghhincome"),
      contains("hhincome_period") & !contains("ghhincome"), # Household income
      contains("betayth_lw") # Calculated longitudinal weights
    )
  return(dataset)
}

# Applying function to all datasets
W9_clean <- clean_data(W9_raw)
W9Y_clean <- clean_data(W9Y_raw)
W9hh_clean <- clean_data(W9hh_raw)
W10_clean <- clean_data(W10_raw)
W10Y_clean <- clean_data(W10Y_raw)
for(i in 1:8){
  assign(paste0("CV", i, "w_clean"), clean_data(get(paste0("CV", i, "w_raw"))))
}
CV2t_clean <- clean_data(CV2t_raw)
CV6t_clean <- clean_data(CV6t_raw)
for(i in c(4, 6, 8)){
  assign(paste0("CV", i, "Y_clean"), clean_data(get(paste0("CV", i, "Y_raw"))))
}

W9hh_clean %<>% dplyr::select(i_hidp, i_fihhmnnet1_dv)

# Removing raw data
rm(list = c("W9_raw", "W9Y_raw", "W9hh_raw", "W10_raw", "W10Y_raw", "CV1w_raw", "CV2w_raw", "CV2t_raw", "CV3w_raw", "CV4w_raw", "CV4Y_raw", "CV5w_raw", "CV6w_raw", "CV6t_raw", "CV6Y_raw", "CV7w_raw", "CV8w_raw", "CV8Y_raw"))
```

# Tidying the data
For ease of use, we convert the data into "tidy" format (where each row represents one observation) and merge the waves into a single data frame. For the COVID-19 survey this is done via the specified function `tidy_COVID`.

```{r tidy}
#######
# Function: tidy_COVID
# Inputs: a cleaned COVID-19 survey dataset and the COVID-19 survey wave number to which the dataset corresponds
# Method: the function removes the wave-demarcating prefix (e.g. "ca_") from variable names and adds a new variable "wave" which encodes this information instead
# Output: a tidied version of the dataset
#######

tidy_COVID <- function(dataset, wave_num){
  names(dataset) <- str_replace(names(dataset), paste0("c", letters[wave_num], "_"), "")
  dataset$wave <- rep(paste0("CV", wave_num), nrow(dataset))
  return(dataset)
}

# Applying function/equivalent code to all datasets except W9 household data
names(W9_clean) <- str_replace(names(W9_clean), "i_", "") # Removing wave indicator
W9_clean$wave <- rep("W9", nrow(W9_clean)) # Making index of waves
names(W9Y_clean) <- str_replace(names(W9Y_clean), "i_", "")
W9Y_clean$wave <- rep("W9", nrow(W9Y_clean))
names(W10_clean) <- str_replace(names(W10_clean), "j_", "")
W10_clean$wave <- rep("W10", nrow(W10_clean))
names(W10Y_clean) <- str_replace(names(W10Y_clean), "j_", "")
W10Y_clean$wave <- rep("W10", nrow(W10Y_clean))
for(i in 1:8){
  assign(paste0("CV", i, "w_clean"), tidy_COVID(get(paste0("CV", i, "w_clean")), i))
}
CV2t_clean <- tidy_COVID(CV2t_clean, 2)
CV6t_clean <- tidy_COVID(CV6t_clean, 6)
for(i in c(4, 6, 8)){
  assign(paste0("CV", i, "Y_clean"), tidy_COVID(get(paste0("CV", i, "Y_clean")), i))
}

# Binding data into one dataset
data_prov <- dplyr::bind_rows(W9_clean, W9Y_clean, W10_clean, W10Y_clean, CV1w_clean, CV2w_clean, CV2t_clean, CV3w_clean, CV4w_clean, CV4Y_clean, CV5w_clean, CV6w_clean, CV6t_clean, CV6Y_clean, CV7w_clean, CV8w_clean, CV8Y_clean)

# Removing individual datasets
rm(list = c("W9_clean", "W9Y_clean", "W10_clean", "W10Y_clean", "CV1w_clean", "CV2w_clean", "CV2t_clean", "CV3w_clean",  "CV4w_clean", "CV4Y_clean", "CV5w_clean", "CV6w_clean", "CV6t_clean", "CV6Y_clean", "CV7w_clean", "CV8w_clean", "CV8Y_clean"))
```

# Stable characteristics
The downloaded data include the file `ukhls_wx/xwavedat.tab`, which indexes the stable characteristics (e.g. sex, birth year, ethnic background) of the participants. These are already checked for consistency and are therefore preferred - so we join the sex, birth year and ethnic background data to the dataset. Sex is recoded such that 0 is male and 1 is female.

```{r stable}
# Reading stable characteristics data
data_stable <- read.delim("Data/Raw/Main_survey/UKDA-6614-tab/tab/ukhls_wx/xwavedat.tab", quote = "")

# Defining NAs
is.na(data_stable[,]) <- data_stable[,] < 0

# Creating a variable to encompass all participant IDs regardless of participant type
data_prov %<>% mutate(pidp = if_else(is.na(pidp), pidp_c, pidp))

# Selecting participant ID, sex, birth year and ethnic background
data_stable %<>% dplyr::select(pidp, sex_dv, birthy, ethn_dv)

# Joining to existing data
data_full <- left_join(data_prov, data_stable, by = "pidp")

# Rendering inconsistent sex_dv values as NA
is.na(data_full$sex_dv) <- data_full$sex_dv == 0

# Checking chsex values for consistency
data_full <- data_full %>% group_by(pidp) %>% mutate(chsex = ifelse(length(unique(chsex)) == 1, unique(chsex), NA))

# Merging chsex into sex_dv where sex_dv is not available
data_full %<>% mutate(sex_merged = sex_dv)

data_full[is.na(data_full$sex_dv),]$sex_merged <- data_full[is.na(data_full$sex_dv),]$chsex

# Converting sex to a factor variable so it is not treated as continuous (0 is male, 1 is female)
data_full %<>% mutate(sex_merged = recode(sex_merged, `1` = 0L, `2` = 1L))

# Removing stable characteristics dataset & provisional dataset
rm(list = c("data_stable", "data_prov"))

# Infilling missing values for stable characteristics
data_full <- data_full %>%
  mutate(i_hidp = if_else(wave == "W9" & !is.na(hidp), hidp, i_hidp)) %>%
  mutate(j_hidp = if_else(wave == "W10" & !is.na(hidp), hidp, j_hidp)) %>%
  group_by(pidp) %>%
  fill(i_hidp, j_hidp, ageon20200815, birthy, sex_merged, ethn_dv, ypschlth1, ypschlth2, .direction = "downup")

# Renaming W9 household income variable for consistency
names(W9hh_clean) <- str_replace(names(W9hh_clean), "i_fihhmnnet1_dv", "fihhmnnet1_dv")

# Merging W9 household income data into dataset
data_W9 <- data_full[data_full$wave == "W9",]
data_W9 <- left_join(data_W9, W9hh_clean, by = "i_hidp")
data_full <- data_full[data_full$wave != "W9",]
data_full <- dplyr::bind_rows(data_full, data_W9)

# Infilling household income within households
data_full[!is.na(data_full$i_hidp),] <- data_full[!is.na(data_full$i_hidp),] %>% group_by(i_hidp, wave) %>% fill(hhincome_amount, hhincome_period, .direction = "downup")
data_full[!is.na(data_full$j_hidp),] <- data_full[!is.na(data_full$j_hidp),] %>% group_by(j_hidp, wave) %>% fill(hhincome_amount, hhincome_period, .direction = "downup")

# Removing W9 household dataset
rm(W9hh_clean)
```

# Saving the long dataset

```{r save_data}
write_csv(data_full, file = "Data/Cleaned/data.csv")
```

# Making data wide again
For longitudinal analyses, it is more convenient for the data to be in "wide" format. So we create such a dataset. Where stable characteristics are only provided for certain waves, we copy the values over so that no participant has multiple rows once duplicate rows are removed.

```{r wide}
data_wide <- data_full %>%
  
  # Widening dataset
  pivot_wider(id_cols = c(pidp, wave), names_from = wave, values_from = !(pidp | pidp_c | pidp | pidpcorrected | sex_merged | ethn_dv | ageon20200815 | birthy | wave | i_hidp | j_hidp | ypschlth1 | ypschlth2), values_fill = NA) %>% 
  
  # Removing rows with no data at all
  select_if(function(x) !all(is.na(x))) %>%
  
  # Joining stable characteristics
  left_join(data_full %>% dplyr::select(pidp, sex_merged, ethn_dv, ageon20200815, birthy, i_hidp, j_hidp, ypschlth1, ypschlth2)) %>%
  
  # Removing duplicate rows
  distinct() %>%
  
  # Calculating COVID monthly household income from amounts and reference periods 
  mutate(
    hhincome_CV4_mutate = case_when(
      hhincome_period_CV4 %in% c(1, 5) ~ hhincome_amount_CV4 * 365/84,
      hhincome_period_CV4 == 2 ~ hhincome_amount_CV4 * 365/168,
      hhincome_period_CV4 == 3 ~ hhincome_amount_CV4,
      hhincome_period_CV4 == 4 ~ hhincome_amount_CV4 / 12
    ),
    hhincome_CV6_mutate = case_when(
      hhincome_period_CV6 %in% c(1, 5) ~ hhincome_amount_CV6 * 365/84,
      hhincome_period_CV6 == 2 ~ hhincome_amount_CV6 * 365/168,
      hhincome_period_CV6 == 3 ~ hhincome_amount_CV6,
      hhincome_period_CV6 == 4 ~ hhincome_amount_CV6 / 12
    ),
    hhincome_CV8_mutate = case_when(
      hhincome_period_CV8 %in% c(1, 5) ~ hhincome_amount_CV8 * 365/84,
      hhincome_period_CV8 == 2 ~ hhincome_amount_CV8 * 365/168,
      hhincome_period_CV8 == 3 ~ hhincome_amount_CV8,
      hhincome_period_CV8 == 4 ~ hhincome_amount_CV8 / 12
    )
  ) %>%

# Calculating mean monthly household income across waves
  rowwise() %>% 
  mutate(mean_income = mean(c(fihhmnnet1_dv_W9, hhincome_CV4_mutate, hhincome_CV6_mutate, hhincome_CV8_mutate), na.rm = TRUE))
```

# Saving the wide dataset

``` {r save_wide_data}
write_csv(data_wide, file = "Data/Cleaned/data_wide.csv")
```