---
title: "3a_analyse_no_controls"
author: "Thomas E. Metherell"
date: "25/08/2021"
output: 
  html_document: 
    keep_md: yes
---

This script analyses the cleaned data from Understanding Society dataset for use in our study of digital exclusion and adolescent mental health during the COVID-19 pandemic in the United Kingdom.

The focus of this analysis is fitting latent growth models to longitudinal SDQ data, including divided by access to a computer and to a good internet connection, without covariates.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Dependencies
We start by loading the necessary dependencies.

```{r dependencies}
library(tidyverse)
library(magrittr)
library(PupillometryR)
library(lavaan)
library(survey)
library(lavaan.survey)
library(scales)
library(cowplot)
library(semTable)
```

# Loading the data
We can now load the cleaned dataset (long and wide versions), and select the waves and variables that are relevant to this analysis.

```{r load_data}
# Loading long dataset
data_full <- read.csv("Data/Cleaned/data.csv", quote = "")

# Loading wide dataset
data_wide <- read.csv("Data/Cleaned/data_wide.csv", quote = "")

# Selecting relevant variables and storing those in data_rel (long data)
data_rel <- data_full[data_full$wave == "W9" | data_full$wave == "CV4" | data_full$wave == "CV6" | data_full$wave == "CV8",] %>% 
  dplyr::select(
    contains("ypsdqtd_dv"), # SDQ summary scores
    wave, # Wave
    pidp, # Participant ID 
    ageon20200815, # Age on 15/08/2020
    sex_merged, # Sex
    contains("ypschlth"), # Digital inclusion variables 
    contains("betayth_lw") # Beta-version longitudinal weights
  )

# Selecting relevant variables and storing those in data_rel_wide (wide data)
data_rel_wide <- data_wide %>% 
  dplyr::select(
    contains("ypsdqtd_dv"), # SDQ summary scores
    pidp, # Participant ID
    ageon20200815, # Age on 15/08/2020
    sex_merged, # Sex 
    ethn_dv, # Ethnicity
    contains("ypschlth"), # Digital inclusion variables 
    contains("betayth_lw"), # Beta-version longitudinal weights
  )

# Removing full datasets
rm(data_full)
rm(data_wide)
```

# Recoding variables
We redefine wave, sex and digital inclusion variables as factors in the long data.

```{r recode}
data_rel$wave <- factor(data_rel$wave, levels = c("W9", "CV4", "CV6", "CV8"))

data_rel$sex_merged <- factor(data_rel$sex_merged)
levels(data_rel$sex_merged) <- c("Male", "Female")

data_rel$ypschlth1 <- factor(data_rel$ypschlth1)
levels(data_rel$ypschlth1) <- c("No", "Yes")
data_rel$ypschlth2 <- factor(data_rel$ypschlth2)
levels(data_rel$ypschlth2) <- c("No", "Yes")
```

# Creating dataset for latent growth models
We specify the data frame `data_sdq`, which contains the data needed for fitting LGMs.

```{r dataset}
# Creating dataset for LGM fitting
data_sdq <- data_rel_wide %>% 
  dplyr::select(
    pidp, # Participant ID
    contains("ypsdqtd_dv"), # Total Difficulties score
    betayth_lw_CV8, # CV8 longitudinal weight 
    ypschlth1, # Access to a computer
    ypschlth2, # Access to a good internet connection
  )

# Renaming SDQ variables to the wave identifiers
names(data_sdq) <- str_replace(names(data_sdq), "ypsdqtd_dv_", "")

# Excluding participants with no CV8 longitudinal weight
data_sdq <- data_sdq[!is.na(data_sdq$betayth_lw_CV8),] 

# Specifying survey weights
survey_design <- svydesign(~0, data = data_sdq, weights = data_sdq$betayth_lw_CV8)
```

# Descriptive plots
We illustrate the mean SDQ scores across the four relevant waves.

```{r plots_1, echo = FALSE}
# Creating index of waves
wave_list<- factor(c("W9", "CV4", "CV6", "CV8"), levels = c("W9", "CV4", "CV6", "CV8"))

# Creating summary of mean SDQ scores
wave <- wave_list
summary_data <- data.frame(wave)

# Calculating means, standard deviations and total numbers of participants
for(i in 1:4){
  summary_data$mean[i] <- mean(data_rel[data_rel$wave == summary_data$wave[i],]$ypsdqtd_dv, na.rm = TRUE)
  summary_data$sd[i] <- sd(data_rel[data_rel$wave == summary_data$wave[i],]$ypsdqtd_dv, na.rm = TRUE)
  summary_data$n[i] <- nrow(data_rel[data_rel$wave == summary_data$wave[i] & !is.na(data_rel$ypsdqtd_dv),])
}

# Calculating standard errors, minimum and maximum values
summary_data %<>% mutate(
  se = sd/sqrt(n), 
  min = mean - se, 
  max = mean + se
)

cat("\n### SDQ summary data")
print(summary_data)

cat("\n### Mean Total Difficulties scores with standard error")
ggplot(summary_data, aes(x = wave, y = mean, group = 1)) +
  annotate(geom = "rect", xmin = 11/6, xmax = 4.5, ymin = -Inf, ymax = Inf, fill = "grey", alpha = 0.3) +
  annotate(geom = "text", x = 4.45, y = 10.6, label = "COVID-19 pandemic", hjust = "right", vjust = "top") +
  geom_line() +
  geom_ribbon(aes(y = NULL, ymin = min, ymax = max), alpha = 0.2) +
  xlab(NULL) +
  ylab("Total Difficulties score") +
  scale_x_discrete(labels = str_wrap(c("2017-19", "July 2020", "November 2020", "March 2021"), width = 15)) +
  theme_classic()
```

```{r plots_2, echo = FALSE, results = "asis"}
cat("\n### Mean Total Difficulties scores with individual trajectories")
ggplot(data_rel, aes(x = wave, y = ypsdqtd_dv, group = pidp)) +
  annotate(geom = "rect", xmin = 11/6, xmax = 4.5, ymin = -Inf, ymax = Inf, fill = "grey", alpha = 0.3) +
  annotate(geom = "text", x = 4.45, y = -0.5, label = "COVID-19 pandemic", hjust = "right", vjust = "top") +
  geom_line(size = 0.02, na.rm = TRUE, alpha = 0.05) +
  geom_flat_violin(aes(group = NULL), colour = NA, fill = "slateblue", adjust = 11/60, na.rm = TRUE) +
  geom_line(data = summary_data, mapping = aes(x = wave, y = mean, group = 1), na.rm = TRUE, size = 1.5) +
  geom_point(data = summary_data, mapping = aes(x = wave, y = mean, group = 1), na.rm = TRUE, size = 3) +
  geom_ribbon(data = summary_data, aes(y = NULL, ymin = min, ymax = max, group = 1), na.rm = TRUE, alpha = 0.2) +
  xlab(NULL) +
  ylab("Mental Health (higher = more difficulties)\n(SDQ Total Difficulties score)") +
  scale_x_discrete(labels = str_wrap(c("2017-19", "July 2020", "November 2020", "March 2021"), width = 15)) +
  theme_classic()

ggsave("Figures/sdq_summary.png")
ggsave("Figures/sdq_summary.svg")
```

# Fitting initial LGM
We now fit a latent growth model to the whole-cohort SDQ data, using pairwise $\chi^2$ tests ($\alpha$ = 0.05) to compare models and accordingly accept or reject sequential changes.

```{r initial_lgm}
# Fitting no-change model
lgm_sdq_nc <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
'

fit_lgm_sdq_nc <- growth(lgm_sdq_nc, data = data_sdq, missing = "fiml")

# Fitting linear model
lgm_sdq_lin <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
'

fit_lgm_sdq_lin <- growth(lgm_sdq_lin, data = data_sdq, missing = "fiml")

# Comparing linear to no-change model
anova(fit_lgm_sdq_lin, fit_lgm_sdq_nc)

# Accepting linear over no-change model

# Fitting quadratic model
lgm_sdq_quad <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8
'

fit_lgm_sdq_quad <- growth(lgm_sdq_quad, data = data_sdq, missing = "fiml")

# Comparing quadratic to linear model
anova(fit_lgm_sdq_quad, fit_lgm_sdq_lin)

# Accepting quadratic over linear model

# Applying weights to model
fit_weighted <- lavaan.survey(fit_lgm_sdq_quad, survey_design, estimator = "ML")

# Summary of weighted model
summary(fit_weighted)

# Producing model output table and exporting to CSV
vlabs <- c("W9" = "Main study wave 9", "CV4" = "COVID-19 wave 4", "CV6" = "COVID-19 wave 6", "CV8" = "COVID-19 wave 8", "i" = "Intercept", "s" = "Linear coefficient", "q" = "Quadratic coefficient")
semTable(fit_weighted, columns = c("estse", "p"), paramSets = c("latentmeans", "latentvariances", "latentcovariances", "residualvariances"), fits = c("chisq", "cfi", "rmsea"), varLabels = vlabs, file = "Data/Objects/undiff_table.csv", type = "csv", print.results = FALSE)

# Saving model fit object
saveRDS(fit_weighted, file = "Data/Objects/undiff.rds")

# Preparing LGM function for plotting
pT <- parTable(fit_weighted)
fit_weighted_fn <- function(x) pT[pT$lhs == "i" & pT$op == "~1",]$est + pT[pT$lhs == "s" & pT$op == "~1",]$est*x + pT[pT$lhs == "q" & pT$op == "~1",]$est*x^2

# Using model parameters to predict individual trajectories
indiv_traj <- data.frame(predict(fit_lgm_sdq_quad))
i <- nrow(indiv_traj)
```

### Final LGM with predicted individual trajectories

``` {r initial_lgm_plot, echo = FALSE}
suppressMessages(
  ggplot() +
    annotate(geom = "rect", xmin = 5/6, xmax = 3.5, ymin = -Inf, ymax = Inf, fill = "grey", alpha = 0.3) +
    annotate(geom = "text", x = 3.45, y = 0, label = "COVID-19 pandemic", hjust = "right", vjust = "top") +
    lapply(1:i, function(i) geom_function(fun = function(x) indiv_traj$i[i] + indiv_traj$s[i] * x + indiv_traj$q[i] * x^2, xlim = c(0, 3), size = 0.5, alpha = 0.05, na.rm = TRUE)) +
    geom_function(data = NULL, mapping = aes(x = NULL, y = NULL, group = NULL), fun = fit_weighted_fn, xlim = c(0, 3), size = 2) +
    scale_x_continuous(breaks = 0:3, limits = c(0, 3.5), labels = c("2017-19", "July 2020", "November 2020", "March 2021")) +
    xlab(NULL) +
    ylab("Total Difficulties score") +
    theme_classic()
)

ggsave("Figures/undiff.png")
ggsave("Figures/undiff.svg")
```

# Grouping by computer access
We now fit a new LGM with the participants grouped by whether or not they have access to a computer.

```{r group_by_computer_access}
# Fitting free model
model_comp_free <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8
'

fit_comp_free <- growth(model_comp_free, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Fitting model with error variances constrained to equality
model_comp_con_ervar <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1_1, ervar1_1)*W9
CV4 ~~ c(ervar2_1, ervar2_1)*CV4
CV6 ~~ c(ervar3_1, ervar3_1)*CV6
CV8 ~~ c(ervar4_1, ervar4_1)*CV8
'

fit_comp_con_ervar <- growth(model_comp_con_ervar, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing model with constrained error variances to free model
anova(fit_comp_con_ervar, fit_comp_free)

# Accepting model with constrained error variances over free model

# Fitting model with constrained y-intercept
model_comp_con_ervar_i <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1_1, ervar1_1)*W9
CV4 ~~ c(ervar2_1, ervar2_1)*CV4
CV6 ~~ c(ervar3_1, ervar3_1)*CV6
CV8 ~~ c(ervar4_1, ervar4_1)*CV8

i ~ c(i_1, i_1)*1
'

fit_comp_con_ervar_i <- growth(model_comp_con_ervar_i, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing model with constrained y-intercept to model without
anova(fit_comp_con_ervar_i, fit_comp_con_ervar)

# Accepting model with constrained y-intercept over model without

# Fitting model with constrained linear coefficient
model_comp_con_ervar_i_s <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1_1, ervar1_1)*W9
CV4 ~~ c(ervar2_1, ervar2_1)*CV4
CV6 ~~ c(ervar3_1, ervar3_1)*CV6
CV8 ~~ c(ervar4_1, ervar4_1)*CV8

i ~ c(i_1, i_1)*1
s ~ c(s_1, s_1)*1
'

fit_comp_con_ervar_i_s <- growth(model_comp_con_ervar_i_s, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing model with constrained linear coefficient to model without
anova(fit_comp_con_ervar_i_s, fit_comp_con_ervar_i)

# Rejecting model with constrained linear coefficient

# Fitting model with constrained quadratic coefficient
model_comp_con_ervar_i_q <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1_1, ervar1_1)*W9
CV4 ~~ c(ervar2_1, ervar2_1)*CV4
CV6 ~~ c(ervar3_1, ervar3_1)*CV6
CV8 ~~ c(ervar4_1, ervar4_1)*CV8

i ~ c(i_1, i_1)*1
q ~ c(q_1, q_1)*1
'

fit_comp_con_ervar_i_q <- growth(model_comp_con_ervar_i_q, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing model with constrained quadratic coefficient to model without
anova(fit_comp_con_ervar_i_q, fit_comp_con_ervar_i)

# Rejecting model with constrained quadratic coefficient
fit_comp_prov <- fit_comp_con_ervar_i

# Fitting model with constrained y-intercept variance
model_comp_con_ivar <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1_1, ervar1_1)*W9
CV4 ~~ c(ervar2_1, ervar2_1)*CV4
CV6 ~~ c(ervar3_1, ervar3_1)*CV6
CV8 ~~ c(ervar4_1, ervar4_1)*CV8

i ~ c(i_1, i_1)*1

i ~~ c(ivar_1, ivar_1)*i
'

fit_comp_con_ivar <- growth(model_comp_con_ivar, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing model with constrained y-intercept variance to model without
anova(fit_comp_con_ivar, fit_comp_prov)

# Accepting model with constrained y-intercept variance over model without

# Fitting model with constrained linear coefficient variance
model_comp_con_ivar_svar <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1_1, ervar1_1)*W9
CV4 ~~ c(ervar2_1, ervar2_1)*CV4
CV6 ~~ c(ervar3_1, ervar3_1)*CV6
CV8 ~~ c(ervar4_1, ervar4_1)*CV8

i ~ c(i_1, i_1)*1

i ~~ c(ivar_1, ivar_1)*i
s ~~ c(svar_1, svar_1)*s
'

fit_comp_con_ivar_svar <- growth(model_comp_con_ivar_svar, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing model with constrained linear coefficient variance to model without
anova(fit_comp_con_ivar_svar, fit_comp_con_ivar)

# Accepting model with constrained linear coefficient variance over model without

# Fitting model with constrained quadratic coefficient variance
model_comp_con_ivar_svar_qvar <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1_1, ervar1_1)*W9
CV4 ~~ c(ervar2_1, ervar2_1)*CV4
CV6 ~~ c(ervar3_1, ervar3_1)*CV6
CV8 ~~ c(ervar4_1, ervar4_1)*CV8

i ~ c(i_1, i_1)*1

i ~~ c(ivar_1, ivar_1)*i
s ~~ c(svar_1, svar_1)*s
q ~~ c(qvar_1, qvar_1)*q
'

fit_comp_con_ivar_svar_qvar <- growth(model_comp_con_ivar_svar_qvar, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing model with constrained quadratic coefficient variance to model without
anova(fit_comp_con_ivar_svar_qvar, fit_comp_con_ivar_svar)

# Accepting model with constrained quadratic coefficient variance over model without
fit_comp_prov <- fit_comp_con_ivar_svar_qvar

# Fitting model with constrained y-intercept/linear coefficient covariance
model_comp_con_iscovar <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1_1, ervar1_1)*W9
CV4 ~~ c(ervar2_1, ervar2_1)*CV4
CV6 ~~ c(ervar3_1, ervar3_1)*CV6
CV8 ~~ c(ervar4_1, ervar4_1)*CV8

i ~ c(i_1, i_1)*1

i ~~ c(ivar_1, ivar_1)*i
s ~~ c(svar_1, svar_1)*s
q ~~ c(qvar_1, qvar_1)*q

i ~~ c(iscovar_1, iscovar_1)*s
'

fit_comp_con_iscovar <- growth(model_comp_con_iscovar, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing model with constrained y-intercept/linear coefficient covariance to model without
anova(fit_comp_con_iscovar, fit_comp_prov)

# Accepting model with constrained y-intercept/linear coefficient covariance over model without

# Fitting model with constrained y-intercept/quadratic coefficient covariance
model_comp_con_iscovar_iqcovar <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1_1, ervar1_1)*W9
CV4 ~~ c(ervar2_1, ervar2_1)*CV4
CV6 ~~ c(ervar3_1, ervar3_1)*CV6
CV8 ~~ c(ervar4_1, ervar4_1)*CV8

i ~ c(i_1, i_1)*1

i ~~ c(ivar_1, ivar_1)*i
s ~~ c(svar_1, svar_1)*s
q ~~ c(qvar_1, qvar_1)*q

i ~~ c(iscovar_1, iscovar_1)*s
i ~~ c(iqcovar_1, iqcovar_1)*q
'

fit_comp_con_iscovar_iqcovar <- growth(model_comp_con_iscovar_iqcovar, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing model with constrained y-intercept/quadratic coefficient covariance to model without
anova(fit_comp_con_iscovar_iqcovar, fit_comp_con_iscovar)

# Accepting model with constrained y-intercept/quadratic coefficient covariance over model without

# Fitting model with constrained linear coefficient/quadratic coefficient covariance
model_comp_con_iscovar_iqcovar_sqcovar <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1_1, ervar1_1)*W9
CV4 ~~ c(ervar2_1, ervar2_1)*CV4
CV6 ~~ c(ervar3_1, ervar3_1)*CV6
CV8 ~~ c(ervar4_1, ervar4_1)*CV8

i ~ c(i_1, i_1)*1

i ~~ c(ivar_1, ivar_1)*i
s ~~ c(svar_1, svar_1)*s
q ~~ c(qvar_1, qvar_1)*q

i ~~ c(iscovar_1, iscovar_1)*s
i ~~ c(iqcovar_1, iqcovar_1)*q
s ~~ c(sqcovar_1, sqcovar_1)*q
'

fit_comp_con_iscovar_iqcovar_sqcovar <- growth(model_comp_con_iscovar_iqcovar_sqcovar, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing model with constrained linear coefficient/quadratic coefficient covariance to model without
anova(fit_comp_con_iscovar_iqcovar_sqcovar, fit_comp_con_iscovar_iqcovar)

# Rejecting model with constrained linear coefficient/quadratic coefficient covariance
fit_comp <- growth(model_comp_con_iscovar_iqcovar, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml")

# Summary of unweighted model
summary(fit_comp)

# Applying weights to model
fit_comp_weighted <- lavaan.survey(fit_comp, survey_design, estimator = "ML")

# Summary of weighted model
summary(fit_comp_weighted)

# Saving model fit object
saveRDS(fit_comp_weighted, file = "Data/Objects/comp_nocov.rds")

# Preparing LGM functions for plotting
pT <- parTable(fit_comp_weighted)
fit_comp_fn0 <- function(x) pT[pT$lhs == "i" & pT$op == "~1" & pT$group == 2,]$est + pT[pT$lhs == "s" & pT$op == "~1" & pT$group == 2,]$est*x + pT[pT$lhs == "q" & pT$op == "~1" & pT$group == 2,]$est*x^2
fit_comp_fn1 <- function(x) pT[pT$lhs == "i" & pT$op == "~1" & pT$group == 1,]$est + pT[pT$lhs == "s" & pT$op == "~1" & pT$group == 1,]$est*x + pT[pT$lhs == "q" & pT$op == "~1" & pT$group == 1,]$est*x^2
```

### Final LGM

``` {r group_by_computer_access_plot_1, echo = FALSE}
suppressMessages(
  ggplot() +
    annotate(geom = "rect", xmin = 5/6, xmax = 3.5, ymin = -Inf, ymax = Inf, fill = "grey", alpha = 0.3) +
    annotate(geom = "text", x = 3.45, y = 10, label = "COVID-19 pandemic", hjust = "right", vjust = "top") +
    geom_function(mapping = aes(colour = "No"), fun = fit_comp_fn0, xlim = c(0, 3), size = 1) +
    geom_function(mapping = aes(colour = "Yes"), fun = fit_comp_fn1, xlim = c(0, 3), size = 1) +
    scale_x_continuous(limits = c(0, 3.5), breaks = 0:3, labels = str_wrap(c("2017-19", "July 2020", "November 2020", "March 2021"), width = 10)) +
    xlab(NULL) +
    ylab("Total Difficulties score") +
    labs(colour = "Has access to a computer", fill = NULL) +
    scale_colour_manual(values = c("No" = "#F8766D", "Yes" = "#00BFC4")) +
    theme_classic()
)
```

# Grouping by internet access
We now fit a new LGM with the participants grouped by whether or not they have access to a "good internet connection".

```{r group_by_internet_access}
# Fitting free model
model_int_free <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8
'

fit_int_free <- growth(model_int_free, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

summary(fit_int_free)

# Fitting model with constrained error variances
model_int_con_ervar <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1_1, ervar1_1)*W9
CV4 ~~ c(ervar2_1, ervar2_1)*CV4
CV6 ~~ c(ervar3_1, ervar3_1)*CV6
CV8 ~~ c(ervar4_1, ervar4_1)*CV8
'

fit_int_con_ervar <- growth(model_int_con_ervar, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing model with constrained error variances to free model
anova(fit_int_con_ervar, fit_int_free)

# Accepting model with constrained error variances over free model

# Fitting model with constrained y-intercept
model_int_con_ervar_i <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1_1, ervar1_1)*W9
CV4 ~~ c(ervar2_1, ervar2_1)*CV4
CV6 ~~ c(ervar3_1, ervar3_1)*CV6
CV8 ~~ c(ervar4_1, ervar4_1)*CV8

i ~ c(i_1, i_1)*1
'

fit_int_con_ervar_i <- growth(model_int_con_ervar_i, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing model with constrained y-intercept to model without
anova(fit_int_con_ervar_i, fit_int_con_ervar)

# Accepting model with constrained y-intercept over model without

# Fitting model with constrained linear coefficient
model_int_con_ervar_i_s <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1_1, ervar1_1)*W9
CV4 ~~ c(ervar2_1, ervar2_1)*CV4
CV6 ~~ c(ervar3_1, ervar3_1)*CV6
CV8 ~~ c(ervar4_1, ervar4_1)*CV8

i ~ c(i_1, i_1)*1
s ~ c(s_1, s_1)*1
'

fit_int_con_ervar_i_s <- growth(model_int_con_ervar_i_s, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing model with constrained linear coefficient to model without
anova(fit_int_con_ervar_i_s, fit_int_con_ervar_i)

# Rejecting model with constrained linear coefficient

# Fitting model with constrained quadratic coefficient
model_int_con_ervar_i_q <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1_1, ervar1_1)*W9
CV4 ~~ c(ervar2_1, ervar2_1)*CV4
CV6 ~~ c(ervar3_1, ervar3_1)*CV6
CV8 ~~ c(ervar4_1, ervar4_1)*CV8

i ~ c(i_1, i_1)*1
q ~ c(q_1, q_1)*1
'

fit_int_con_ervar_i_q <- growth(model_int_con_ervar_i_q, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing model with constrained quadratic coefficient to model without
anova(fit_int_con_ervar_i_q, fit_int_con_ervar_i)

# Accepting model with constrained quadratic coefficient over model without
fit_int_prov <- fit_int_con_ervar_i_q

# Fitting model with constrained y-intercept variance
model_int_con_ivar <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1_1, ervar1_1)*W9
CV4 ~~ c(ervar2_1, ervar2_1)*CV4
CV6 ~~ c(ervar3_1, ervar3_1)*CV6
CV8 ~~ c(ervar4_1, ervar4_1)*CV8

i ~ c(i_1, i_1)*1
q ~ c(q_1, q_1)*1

i ~~ c(ivar_1, ivar_1)*i
'

fit_int_con_ivar <- growth(model_int_con_ivar, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing model with constrained y-intercept variance to model without
anova(fit_int_con_ivar, fit_int_prov)

# Accepting model with constrained y-intercept variance over model without

# Fitting model with constrained linear coefficient variance
model_int_con_ivar_svar <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1_1, ervar1_1)*W9
CV4 ~~ c(ervar2_1, ervar2_1)*CV4
CV6 ~~ c(ervar3_1, ervar3_1)*CV6
CV8 ~~ c(ervar4_1, ervar4_1)*CV8

i ~ c(i_1, i_1)*1
q ~ c(q_1, q_1)*1

i ~~ c(ivar_1, ivar_1)*i
s ~~ c(svar_1, svar_1)*s
'

fit_int_con_ivar_svar <- growth(model_int_con_ivar_svar, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing model with constrained linear coefficient variance to model without
anova(fit_int_con_ivar_svar, fit_int_con_ivar)

# Accepting model with constrained linear coefficient variance over model without

# Fitting model with constrained quadratic coefficient variance
model_int_con_ivar_svar_qvar <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1_1, ervar1_1)*W9
CV4 ~~ c(ervar2_1, ervar2_1)*CV4
CV6 ~~ c(ervar3_1, ervar3_1)*CV6
CV8 ~~ c(ervar4_1, ervar4_1)*CV8

i ~ c(i_1, i_1)*1
q ~ c(q_1, q_1)*1

i ~~ c(ivar_1, ivar_1)*i
s ~~ c(svar_1, svar_1)*s
q ~~ c(qvar_1, qvar_1)*q
'

fit_int_con_ivar_svar_qvar <- growth(model_int_con_ivar_svar_qvar, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing model with constrained quadratic coefficient variance to model without
anova(fit_int_con_ivar_svar_qvar, fit_int_con_ivar_svar)

# Rejecting model with constrained quadratic coefficient variance
fit_int_prov <- fit_int_con_ivar_svar

# Fitting model with constrained y-intercept/linear coefficient covariance
model_int_con_iscovar <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1_1, ervar1_1)*W9
CV4 ~~ c(ervar2_1, ervar2_1)*CV4
CV6 ~~ c(ervar3_1, ervar3_1)*CV6
CV8 ~~ c(ervar4_1, ervar4_1)*CV8

i ~ c(i_1, i_1)*1
q ~ c(q_1, q_1)*1

i ~~ c(ivar_1, ivar_1)*i
s ~~ c(svar_1, svar_1)*s

i ~~ c(iscovar_1, iscovar_1)*s
'

fit_int_con_iscovar <- growth(model_int_con_iscovar, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing model with constrained y-intercept/linear coefficient covariance to model without
anova(fit_int_con_iscovar, fit_int_prov)

# Accepting model with constrained y-intercept/linear coefficient covariance over model without

# Fitting model with constrained y-intercept/quadratic coefficient covariance
model_int_con_iscovar_iqcovar <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1_1, ervar1_1)*W9
CV4 ~~ c(ervar2_1, ervar2_1)*CV4
CV6 ~~ c(ervar3_1, ervar3_1)*CV6
CV8 ~~ c(ervar4_1, ervar4_1)*CV8

i ~ c(i_1, i_1)*1
q ~ c(q_1, q_1)*1

i ~~ c(ivar_1, ivar_1)*i
s ~~ c(svar_1, svar_1)*s

i ~~ c(iscovar_1, iscovar_1)*s
i ~~ c(iqcovar_1, iqcovar_1)*q
'

fit_int_con_iscovar_iqcovar <- growth(model_int_con_iscovar_iqcovar, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing model with constrained y-intercept/quadratic coefficient covariance to model without
anova(fit_int_con_iscovar_iqcovar, fit_int_con_iscovar)

# Accepting model with constrained y-intercept/quadratic coefficient covariance over model without

# Fitting model with constrained linear coefficient/quadratic coefficient covariance
model_int_con_iscovar_iqcovar_sqcovar <- '
i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1_1, ervar1_1)*W9
CV4 ~~ c(ervar2_1, ervar2_1)*CV4
CV6 ~~ c(ervar3_1, ervar3_1)*CV6
CV8 ~~ c(ervar4_1, ervar4_1)*CV8

i ~ c(i_1, i_1)*1
q ~ c(q_1, q_1)*1

i ~~ c(ivar_1, ivar_1)*i
s ~~ c(svar_1, svar_1)*s

i ~~ c(iscovar_1, iscovar_1)*s
i ~~ c(iqcovar_1, iqcovar_1)*q
s ~~ c(sqcovar_1, sqcovar_1)*q
'

fit_int_con_iscovar_iqcovar_sqcovar <- growth(model_int_con_iscovar_iqcovar_sqcovar, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing model with constrained linear coefficient/quadratic coefficient covariance to model without
anova(fit_int_con_iscovar_iqcovar_sqcovar, fit_int_con_iscovar_iqcovar)

# Rejecting model with constrained linear coefficient/quadratic coefficient covariance
fit_int <- growth(model_int_con_iscovar_iqcovar, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml")

# Summary of unweighted model
summary(fit_int)

# Applying weights to model
fit_int_weighted <- lavaan.survey(fit_int, survey_design, estimator = "ML")

# Summary of weighted model
summary(fit_int_weighted)

# Saving model fit object
saveRDS(fit_int_weighted, file = "Data/Objects/int_nocov.rds")

# Preparing LGM functions for plotting
pT <- parTable(fit_int_weighted)
fit_int_fn0 <- function(x) pT[pT$lhs == "i" & pT$op == "~1" & pT$group == 2,]$est + pT[pT$lhs == "s" & pT$op == "~1" & pT$group == 2,]$est*x + pT[pT$lhs == "q" & pT$op == "~1" & pT$group == 2,]$est*x^2
fit_int_fn1 <- function(x) pT[pT$lhs == "i" & pT$op == "~1" & pT$group == 1,]$est + pT[pT$lhs == "s" & pT$op == "~1" & pT$group == 1,]$est*x + pT[pT$lhs == "q" & pT$op == "~1" & pT$group == 1,]$est*x^2
```

### Final LGM

``` {r group_by_internet_access_plot_1, echo = FALSE}
suppressMessages(
  ggplot() +
    annotate(geom = "rect", xmin = 5/6, xmax = 3.5, ymin = -Inf, ymax = Inf, fill = "grey", alpha = 0.3) +
    annotate(geom = "text", x = 3.45, y = 10, label = "COVID-19 pandemic", hjust = "right", vjust = "top") +
    geom_function(mapping = aes(colour = "No"), fun = fit_int_fn0, xlim = c(0, 3), size = 1) +
    geom_function(mapping = aes(colour = "Yes"), fun = fit_int_fn1, xlim = c(0, 3), size = 1) +
    scale_x_continuous(limits = c(0, 3.5), breaks = 0:3, labels = str_wrap(c("2017-19", "July 2020", "November 2020", "March 2021"), width = 10)) +
    xlab(NULL) +
    ylab("Total Difficulties score") +
    labs(colour = str_wrap("Has access to a good internet connection", width = 20), fill = NULL) +
    scale_colour_manual(values = c("No" = "#F8766D", "Yes" = "#00BFC4")) +
    theme_classic()
)
```