---
title: "2_sample_characteristics"
author: "Thomas E. Metherell"
date: "06/10/2021"
output: 
  html_document: 
    keep_md: yes
---

This script reports the sample characteristics for our study of digital exclusion and adolescent mental health during the COVID-19 pandemic in the United Kingdom.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Dependencies
We start by loading the necessary dependencies.

```{r dependencies}
library(tidyverse)
library(magrittr)
```

# Loading the data
We can now load the wide dataset.

```{r load_data}
# Loading wide dataset
data_wide <- read.csv("Data/Cleaned/data_wide.csv", quote = "")
```

# Reporting sample characteristics
Below are selected summaries of sample characteristics. Some numbers are suppressed to protect individual participant identities.

``` {r sample_characteristics_1, echo = FALSE, results = "asis"}
# Number of participants with CV8 longitudinal weight
data_wide <- data_wide[!is.na(data_wide$betayth_lw_CV8),]
cat(paste("Number of participants with CV8 longitudinal weight:", nrow(data_wide), "\n\n"))

# Number of participants also with at least one Total Difficulties score
data_wide <- data_wide[!is.na(data_wide$ypsdqtd_dv_W9) | !is.na(data_wide$ypsdqtd_dv_CV4) | !is.na(data_wide$ypsdqtd_dv_CV6) | !is.na(data_wide$ypsdqtd_dv_CV8),]
cat(paste("Number of participants also with at least one Total Difficulties score:", nrow(data_wide)))

write_csv(data_wide, "Data/Cleaned/sample.csv")
```

```{r sample_characteristics_2, echo = FALSE}
# Tabulating characteristics of inclusion groups
data_tab <- data_wide %>% dplyr::select(
  pidp,
  ypschlth1,
  ypschlth2,
  sex_merged,
  birthy,
  ethn_dv,
  fihhmnnet1_dv_W9,
  mean_income,
  contains("ypsdqtd_dv")
)

# Removing initial dataset
rm(data_wide)

data_tab %<>% mutate(
  
  # Grouping mean income into classes
  mean_income_class = case_when(
    mean_income < 20000/12 ~ "< 20000",
    20000/12 <= mean_income & mean_income < 30000/12 ~ "20000-30000",
    30000/12 <= mean_income & mean_income < 40000/12 ~ "30000-40000",
    40000/12 <= mean_income & mean_income < 50000/12 ~ "40000-50000",
    50000/12 <= mean_income ~ ">= 50000"
  ),
  
  # Grouping ethnicity into classes
  ethn_dv_class = case_when(
    ethn_dv == 1 ~ "White British",
    2 <= ethn_dv & ethn_dv <= 4 ~ "Other White",
    5 <= ethn_dv & ethn_dv <= 8 ~ "Mixed",
    9 <= ethn_dv & ethn_dv <= 13 ~ "Asian",
    14 <= ethn_dv & ethn_dv <= 16 ~ "Black",
    ethn_dv == 17 | ethn_dv == 97 ~ "Other"
  ),
  
  # Creating a birth year variable to be made a factor variable
  birthy_class = birthy
)

# Rendering characteristics as factor variables
data_tab$sex_merged <- factor(data_tab$sex_merged)
data_tab$birthy_class <- factor(data_tab$birthy_class)
data_tab$ethn_dv_class <- factor(data_tab$ethn_dv_class)
data_tab$mean_income_class <- factor(data_tab$mean_income_class)

# Selecting relevant data
data_tab %<>% dplyr::select(
  ypschlth1,
  ypschlth2,
  sex_merged,
  birthy_class,
  ethn_dv_class,
  mean_income_class,
  contains("ypsdqtd_dv")
)

# Temporarily merging "Other" ethnicity group into NA
data_temp <- data_tab %>% mutate(
  ethn_dv_class = ifelse(ethn_dv_class == "Other", NA, ethn_dv_class)
)

# Re-rendering ethnicity as a factor variable
data_temp$ethn_dv_class <- factor(data_temp$ethn_dv_class, labels = c("Asian", "Black", "Mixed", "Other White", "White British"))

cat("All participants")
nrow(data_temp)
summary(data_temp %>% select(!contains("yp")), maxsum = Inf)

# Temporarily merging "Other" ethnicity group into NA and income above £50,000 into NA
data_temp <- data_tab %>% mutate(
  ethn_dv_class = ifelse(ethn_dv_class == "Other", NA, ethn_dv_class),
  mean_income_class = ifelse(mean_income_class == ">= 50000", NA, mean_income_class)
)

# Re-rendering ethnicity and income as factor variables
data_temp$ethn_dv_class <- factor(data_temp$ethn_dv_class, labels = c("Asian", "Black", "Mixed", "Other White", "White British"))
data_temp$mean_income_class <- factor(data_temp$mean_income_class, labels = c("< 20000", "20000-30000", "30000-40000", "40000-50000"))

cat("Has W9 SDQ score")
nrow(data_temp[!is.na(data_temp$ypsdqtd_dv_W9),])
summary(data_temp[!is.na(data_temp$ypsdqtd_dv_W9),] %>% select(!contains("yp")), maxsum = Inf)

cat("Does not have W9 SDQ score")
nrow(data_temp[is.na(data_temp$ypsdqtd_dv_W9),])
summary(data_temp[is.na(data_temp$ypsdqtd_dv_W9),] %>% select(!contains("yp")), maxsum = Inf)

# Temporarily merging "Other" ethnicity group into NA 
data_temp <- data_tab %>% mutate(
  ethn_dv_class = ifelse(ethn_dv_class == "Other", NA, ethn_dv_class)
)

# Re-rendering ethnicity as a factor variables
data_temp$ethn_dv_class <- factor(data_temp$ethn_dv_class, labels = c("Asian", "Black", "Mixed", "Other White", "White British"))

cat("Has CV4 SDQ score")
nrow(data_temp[!is.na(data_temp$ypsdqtd_dv_CV4),])
summary(data_temp[!is.na(data_temp$ypsdqtd_dv_CV4),] %>% select(!contains("yp")), maxsum = Inf)

cat("Does not have CV4 SDQ score")
nrow(data_temp[is.na(data_temp$ypsdqtd_dv_CV4),])
summary(data_temp[is.na(data_temp$ypsdqtd_dv_CV4),] %>% select(!contains("yp")), maxsum = Inf)

cat("Has CV6 SDQ score")
nrow(data_temp[!is.na(data_temp$ypsdqtd_dv_CV6),])
summary(data_temp[!is.na(data_temp$ypsdqtd_dv_CV6),] %>% select(!contains("yp")), maxsum = Inf)

cat("Does not have CV6 SDQ score")
nrow(data_temp[is.na(data_temp$ypsdqtd_dv_CV6),])
summary(data_temp[is.na(data_temp$ypsdqtd_dv_CV6),] %>% select(!contains("yp")), maxsum = Inf)

cat("Has CV8 SDQ score")
nrow(data_temp[!is.na(data_temp$ypsdqtd_dv_CV8),])

cat("Does not have CV8 SDQ score")
nrow(data_temp[is.na(data_temp$ypsdqtd_dv_CV8),])

data_tab %<>% mutate(
  
  # Re-grouping mean income
  mean_income_class = case_when(
    mean_income_class %in% c("< 20000", "20000-30000", "30000-40000") ~ "< 40000",
    mean_income_class %in% c("40000-50000", ">= 50000") ~ ">= 40000"
  ),
  
  # Re-grouping ethnicity
  ethn_dv_class = case_when(
    ethn_dv_class %in% c("White British", "Other White") ~ "White",
    ethn_dv_class %in% c("Mixed", "Asian", "Black", "Other") ~ "Non-White"
  ),
  
  # Grouping birth year
  birthy_class = case_when(
    birthy_class %in% c("2004", "2005", "2006", "2007") ~ "2004-07",
    birthy_class %in% c("2008", "2009", "2010", "2011") ~ "2008-11"
  )
)

# Re-rendering birth year, ethnicity and mean income as factor variables
data_tab$birthy_class <- factor(data_tab$birthy_class)
data_tab$ethn_dv_class <- factor(data_tab$ethn_dv_class)
data_tab$mean_income_class <- factor(data_tab$mean_income_class)

cat("All participants")
nrow(data_tab)
summary(data_tab %>% select(!contains("yp")), maxsum = Inf)

cat("Participants with digital inclusion response")
nrow(data_tab[!is.na(data_tab$ypschlth1),])
summary(data_tab[!is.na(data_tab$ypschlth1),] %>% select(!ethn_dv_class & !contains("yp")), maxsum = Inf)

cat("Participants without digital inclusion response")
nrow(data_tab[is.na(data_tab$ypschlth1),])
summary(data_tab[is.na(data_tab$ypschlth1),] %>% select(!ethn_dv_class & !contains("yp")), maxsum = Inf)

# Excluding participants with no response to the digital inclusion question
data_tab <- data_tab[!is.na(data_tab$ypschlth1),]

cat("Computer = 1, Internet = 1")
nrow(data_tab[data_tab$ypschlth1 == 1 & data_tab$ypschlth2 == 1,])
summary(data_tab[data_tab$ypschlth1 == 1 & data_tab$ypschlth2 == 1,] %>% select(!ethn_dv_class & !contains("yp")), maxsum = Inf)

cat("All other responses")
nrow(data_tab[!(data_tab$ypschlth1 == 1 & data_tab$ypschlth2 == 1),])
summary(data_tab[!(data_tab$ypschlth1 == 1 & data_tab$ypschlth2 == 1),] %>% select(!ethn_dv_class & !contains("yp")), maxsum = Inf)
```