---
title: "5_sensitivity_check"
author: "Thomas E. Metherell"
date: "17/10/2021"
output: 
  html_document: 
    keep_md: yes
---

This script is used for modelling of data for all respondents with a response to the digital inclusion question (not just those with a CV8 longitudinal weight) - this is used as a sensitivity check for our analyses.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Dependencies
We start by loading the necessary dependencies.

```{r dependencies}
library(tidyverse)
library(magrittr)
library(scales)
library(lavaan)
library(survey)
library(lavaan.survey)
library(visdat)
library(semTable)
```

# Loading the data
We can now load the cleaned dataset (wide version), and select the waves and variables that are relevant to this analysis.

```{r load_data}
# Loading wide dataset
data_wide <- read.csv("Data/Cleaned/data_wide.csv", quote = "")

# Selecting relevant variables and storing those in data_rel_wide
data_rel_wide <- data_wide %>% 
  dplyr::select(
    contains("ypsdqtd_dv"), # SDQ summary scores
    pidp, # Participant ID
    ageon20200815, # Age on 15/08/2020
    sex_merged, # Sex 
    birthy, # Birth year
    ethn_dv, # Ethnicity
    mean_income, # Mean household income
    contains("ypschlth"), # Digital inclusion variables 
    contains("betayth_lw") # Beta-version longitudinal weights
  )

# Removing full dataset
rm(data_wide)
```

# Creating dataset for latent growth models
We specify the data frame `data_sdq`, which contains the data needed for fitting LGMs.

```{r dataset}
# Creating dataset for LGM fitting
data_sdq <- data_rel_wide %>% 
  dplyr::select(
    pidp, # Participant ID
    contains("ypsdqtd_dv"), # Total Difficulties score
    sex_merged, # Sex
    birthy, # Birth year
    ethn_dv, # Ethnicity
    mean_income, # Mean household income
    betayth_lw_CV8, # CV8 longitudinal weight 
    ypschlth1, # Access to a computer
    ypschlth2 # Access to a good internet connection
  )

# NOT excluding participants with no CV8 longitudinal weight

# Excluding participants with no response to digital inclusion question
data_sdq <- data_sdq[!is.na(data_sdq$ypschlth1),]

# Renaming SDQ variables to the wave identifiers
names(data_sdq) <- str_replace(names(data_sdq), "ypsdqtd_dv_", "")

data_sdq %<>% mutate(
  # Coding ethnicity as a dichotomous variable ("white or not")
  ethn_caucasian = if_else(ethn_dv == (1 | 2 | 3 | 4), 1, 0)
)

# Rescaling birth year between 0 and 1
data_sdq$birthy <- rescale(data_sdq$birthy, to = c(0,1))

# Rescaling mean income between 0 and 1
data_sdq$mean_income <- rescale(data_sdq$mean_income, to = c(0,1))
```

# Visualising missing data

```{r missing, echo = FALSE}
vis_miss(data_sdq %>% dplyr::select(mean_income, sex_merged, birthy, ethn_caucasian, W9, CV4, CV6, CV8))
```

# Fitting models grouped by computer access with covariates
We now fit a new LGM with the participants grouped by whether or not they have access to a computer, and controlling for sex, birth year, ethnicity and mean household income.

``` {r computer_covariates}
# Fitting no-change model
model_comp_nc <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8

i ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_comp_nc <- growth(model_comp_nc, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Fitting linear model
model_comp_lin <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_comp_lin <- growth(model_comp_lin, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing linear to no-change model
anova(fit_comp_lin, fit_comp_nc)

# Accepting linear over no-change model

# Fitting quadratic model
model_comp_quad <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_comp_quad <- growth(model_comp_quad, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing quadratic to linear model
anova(fit_comp_quad, fit_comp_lin)

# Accepting quadratic over linear model

# Fitting model with error variances constrained to equality
model_comp_con_ervar <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1, ervar1) * W9
CV4 ~~ c(ervar2, ervar2) * CV4
CV6 ~~ c(ervar3, ervar3) * CV6
CV8 ~~ c(ervar4, ervar4) * CV8

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_comp_con_ervar <- growth(model_comp_con_ervar, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing model with constrained error variances to free model
anova(fit_comp_con_ervar, fit_comp_quad)

# Accepting model with constrained error variances over model without

# Fitting model with constrained y-intercept
model_comp_con_ervar_i <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1, ervar1) * W9
CV4 ~~ c(ervar2, ervar2) * CV4
CV6 ~~ c(ervar3, ervar3) * CV6
CV8 ~~ c(ervar4, ervar4) * CV8
 
i ~ c(i_1, i_1) * 1

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_comp_con_ervar_i <- growth(model_comp_con_ervar_i, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing model with constrained y-intercept to free model
anova(fit_comp_con_ervar_i, fit_comp_con_ervar)

# Accepting model with constrained y-intercept over free model

# Fitting model with constrained linear coefficient
model_comp_con_ervar_i_s <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1, ervar1) * W9
CV4 ~~ c(ervar2, ervar2) * CV4
CV6 ~~ c(ervar3, ervar3) * CV6
CV8 ~~ c(ervar4, ervar4) * CV8
 
i ~ c(i_1, i_1) * 1
s ~ c(s_1, s_1) * 1

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_comp_con_ervar_i_s <- growth(model_comp_con_ervar_i_s, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing model with constrained linear coefficient to model without
anova(fit_comp_con_ervar_i_s, fit_comp_con_ervar_i)

# Rejecting model with constrained linear coefficient

# Fitting model with constrained quadratic coefficient
model_comp_con_ervar_i_q <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8
 
W9 ~~ c(ervar1, ervar1) * W9
CV4 ~~ c(ervar2, ervar2) * CV4
CV6 ~~ c(ervar3, ervar3) * CV6
CV8 ~~ c(ervar4, ervar4) * CV8

i ~ c(i_1, i_1) * 1
q ~ c(q_1, q_1) * 1

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_comp_con_ervar_i_q <- growth(model_comp_con_ervar_i_q, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing model with constrained quadratic coefficient to model without
anova(fit_comp_con_ervar_i_q, fit_comp_con_ervar_i)

# Rejecting model with constrained quadratic coefficient
fit_comp_prov <- fit_comp_con_ervar_i

# Fitting model with constrained y-intercept variance
model_comp_con_ivar <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1, ervar1) * W9
CV4 ~~ c(ervar2, ervar2) * CV4
CV6 ~~ c(ervar3, ervar3) * CV6
CV8 ~~ c(ervar4, ervar4) * CV8
 
i ~ c(i_1, i_1) * 1

i ~~ c(ivar, ivar) * i

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_comp_con_ivar <- growth(model_comp_con_ivar, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing model with constrained y-intercept variance to model without
anova(fit_comp_con_ivar, fit_comp_prov)

# Accepting model with constrained y-intercept variance over model without

# Fitting model with constrained linear coefficient variance
model_comp_con_ivar_svar <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1, ervar1) * W9
CV4 ~~ c(ervar2, ervar2) * CV4
CV6 ~~ c(ervar3, ervar3) * CV6
CV8 ~~ c(ervar4, ervar4) * CV8
 
i ~ c(i_1, i_1) * 1

i ~~ c(ivar, ivar) * i
s ~~ c(svar, svar) * s

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_comp_con_ivar_svar <- growth(model_comp_con_ivar_svar, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing model with constrained linear coefficient variance to model without
anova(fit_comp_con_ivar_svar, fit_comp_con_ivar)

# Accepting model with constrained linear coefficient variance over model without

# Fitting model with constrained quadratic coefficient variance
model_comp_con_ivar_svar_qvar <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1, ervar1) * W9
CV4 ~~ c(ervar2, ervar2) * CV4
CV6 ~~ c(ervar3, ervar3) * CV6
CV8 ~~ c(ervar4, ervar4) * CV8
 
i ~ c(i_1, i_1) * 1

i ~~ c(ivar, ivar) * i
s ~~ c(svar, svar) * s
q ~~ c(qvar, qvar) * q

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_comp_con_ivar_svar_qvar <- growth(model_comp_con_ivar_svar_qvar, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing model with constrained quadratic coefficient variance to model without
anova(fit_comp_con_ivar_svar_qvar, fit_comp_con_ivar_svar)

# Accepting model with constrained quadratic coefficient variance
fit_comp_prov <- fit_comp_con_ivar_svar_qvar

# Fitting model with constrained y-intercept/linear coefficient covariance
model_comp_con_iscovar <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1, ervar1) * W9
CV4 ~~ c(ervar2, ervar2) * CV4
CV6 ~~ c(ervar3, ervar3) * CV6
CV8 ~~ c(ervar4, ervar4) * CV8
 
i ~ c(i_1, i_1) * 1

i ~~ c(ivar, ivar) * i
s ~~ c(svar, svar) * s
q ~~ c(qvar, qvar) * q

i ~~ c(iscovar, iscovar) * s

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_comp_con_iscovar <- growth(model_comp_con_iscovar, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing model with constrained y-intercept/linear coefficient covariance to model without
anova(fit_comp_con_iscovar, fit_comp_prov)

# Accepting model with constrained y-intercept/linear coefficient covariance over model without

# Fitting model with constrained y-intercept/quadratic coefficient covariance
model_comp_con_iscovar_iqcovar <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1, ervar1) * W9
CV4 ~~ c(ervar2, ervar2) * CV4
CV6 ~~ c(ervar3, ervar3) * CV6
CV8 ~~ c(ervar4, ervar4) * CV8
 
i ~ c(i_1, i_1) * 1

i ~~ c(ivar, ivar) * i
s ~~ c(svar, svar) * s
q ~~ c(qvar, qvar) * q

i ~~ c(iscovar, iscovar) * s
i ~~ c(iqcovar, iqcovar) * q

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_comp_con_iscovar_iqcovar <- growth(model_comp_con_iscovar_iqcovar, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing model with constrained y-intercept/quadratic coefficient covariance to model without
anova(fit_comp_con_iscovar_iqcovar, fit_comp_con_iscovar)

# Accepting model with constrained y-intercept/quadratic coefficient covariance over model without

# Fitting model with constrained linear coefficient/quadratic coefficient covariance
model_comp_con_iscovar_iqcovar_sqcovar <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8
 
i ~ c(i_1, i_1) * 1

W9 ~~ c(ervar1, ervar1) * W9
CV4 ~~ c(ervar2, ervar2) * CV4
CV6 ~~ c(ervar3, ervar3) * CV6
CV8 ~~ c(ervar4, ervar4) * CV8

i ~~ c(ivar, ivar) * i
s ~~ c(svar, svar) * s
q ~~ c(qvar, qvar) * q

i ~~ c(iscovar, iscovar) * s
i ~~ c(iqcovar, iqcovar) * q
s ~~ c(sqcovar, sqcovar) * q

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_comp_con_iscovar_iqcovar_sqcovar <- growth(model_comp_con_iscovar_iqcovar_sqcovar, data = data_sdq[!is.na(data_sdq$ypschlth1),], group = "ypschlth1", missing = "fiml", estimator = "mlr")

# Comparing model with constrained linear coefficient/quadratic coefficient covariance to model without
anova(fit_comp_con_iscovar_iqcovar_sqcovar, fit_comp_con_iscovar_iqcovar)

# Accepting model with constrained linear coefficient/quadratic coefficient covariance over model without
fit_comp <- fit_comp_con_iscovar_iqcovar_sqcovar

# Summary of unweighted model
summary(fit_comp)

# Tabulating model output
vlabs <- c("W9" = "Main study wave 9", "CV4" = "COVID-19 wave 4", "CV6" = "COVID-19 wave 6", "CV8" = "COVID-19 wave 8", "i" = "Intercept", "s" = "Linear coefficient", "q" = "Quadratic coefficient", "sex_merged" = "Sex", "birthy" = "Birth year", "ethn_caucasian" = "Dichotomised ethnicity", "mean_income" = "Mean monthly household income")

semTable(fit_comp, columns = c("estse", "p"), paramSets = c("latentmeans", "latentvariances", "latentcovariances", "residualvariances"), fits = c("chisq", "cfi", "rmsea"), varLabels = vlabs, file = "Data/Objects/sens_check_comp_table.csv", type = "csv", print.results = FALSE)

# Saving model fit object
saveRDS(fit_comp, file = "Data/Objects/sens_check_comp.rds")

# Preparing unweighted LGM functions for plotting
pT <- parTable(fit_comp)
pT %<>% mutate(maxv = est + se, minv = est - se)
fit_comp_fn0 <- function(x) pT[pT$lhs == "i" & pT$op == "~1" & pT$group == 2,]$est + pT[pT$lhs == "s" & pT$op == "~1" & pT$group == 2,]$est*x + pT[pT$lhs == "q" & pT$op == "~1" & pT$group == 2,]$est*x^2
fit_comp_fn1 <- function(x) pT[pT$lhs == "i" & pT$op == "~1" & pT$group == 1,]$est + pT[pT$lhs == "s" & pT$op == "~1" & pT$group == 1,]$est*x + pT[pT$lhs == "q" & pT$op == "~1" & pT$group == 1,]$est*x^2

# Using LGM parameters to predict individual trajectories
indiv_traj_p <- predict(fit_comp)

# Extracting predicted individual trajectory data
indiv_traj0 <- data.frame(indiv_traj_p[["0"]])
indiv_traj1 <- data.frame(indiv_traj_p[["1"]])
i <- nrow(indiv_traj0)
j <- nrow(indiv_traj1)
```

### Final LGM (unweighted)

```{r computer_covariates_plot_1, echo = FALSE}
suppressMessages(
  ggplot() +
    annotate(geom = "rect", xmin = 5/6, xmax = 3.5, ymin = -Inf, ymax = Inf, fill = "grey", alpha = 0.3) +
    annotate(geom = "text", x = 3.45, y = 9, label = "COVID-19 pandemic", hjust = "right", vjust = "top") +
    geom_function(mapping = aes(colour = "No"), fun = fit_comp_fn0, xlim = c(0, 3), size = 1) +
    geom_function(mapping = aes(colour = "Yes"), fun = fit_comp_fn1, xlim = c(0, 3), size = 1) +
    scale_x_continuous(limits = c(0, 3.5), breaks = 0:3, labels = str_wrap(c("2017-19", "July 2020", "November 2020", "March 2021"), width = 10)) +
    ylim(9, 19) +
    xlab(NULL) +
    ylab("Total Difficulties score") +
    labs(colour = "Has access to a computer", fill = NULL) +
    scale_colour_manual(values = c("No" = "#F8766D", "Yes" = "#00BFC4")) +
    theme_classic()
)
ggsave("Figures/comp_sens.png")
ggsave("Figures/comp_sens.svg")
```

### Final LGM (unweighted, by group with predicted individual trajectories)

```{r computer_covariates_plot_2, echo = FALSE}
suppressMessages(
  ggplot() +
    annotate(geom = "rect", xmin = 5/6, xmax = 3.5, ymin = -Inf, ymax = Inf, fill = "grey", alpha = 0.3) +
    annotate(geom = "text", x = 3.45, y = 0, label = "COVID-19 pandemic", hjust = "right", vjust = "top") +
    lapply(1:i, function(i) geom_function(fun = function(x) indiv_traj0$i[i] + indiv_traj0$s[i] * x + indiv_traj0$q[i] * x^2, mapping = aes(colour = "No"), xlim = c(0, 3), size = 0.5, alpha = 20/nrow(indiv_traj0))) +
    geom_function(mapping = aes(colour = "No"), fun = fit_comp_fn0, xlim = c(0, 3), size = 2) +
    scale_x_continuous(limits = c(0, 3.5), breaks = 0:3, labels = str_wrap(c("2017-19", "July 2020", "November 2020", "March 2021"), width = 10)) +
    xlab(NULL) +
    ylab("Total Difficulties score") +
    labs(colour = "Has access to a computer", fill = NULL) +
    scale_colour_manual(values = c("No" = "#F8766D")) +
    theme_classic()
)

suppressMessages(
  ggplot() +
    annotate(geom = "rect", xmin = 5/6, xmax = 3.5, ymin = -Inf, ymax = Inf, fill = "grey", alpha = 0.3) +
    annotate(geom = "text", x = 3.45, y = 0, label = "COVID-19 pandemic", hjust = "right", vjust = "top") +
    lapply(1:j, function(j) geom_function(fun = function(x) indiv_traj1$i[j] + indiv_traj1$s[j] * x + indiv_traj1$q[j] * x^2, mapping = aes(colour = "Yes"), xlim = c(0, 3), size = 0.5, alpha = 20/nrow(indiv_traj1))) +
    geom_function(mapping = aes(colour = "Yes"), fun = fit_comp_fn1, xlim = c(0, 3), size = 2) +
    scale_x_continuous(limits = c(0, 3.5), breaks = 0:3, labels = str_wrap(c("2017-19", "July 2020", "November 2020", "March 2021"), width = 10)) +
    xlab(NULL) +
    ylab("Total Difficulties score") +
    labs(colour = "Has access to a computer", fill = NULL) +
    scale_colour_manual(values = c("Yes" = "#00BFC4")) +
    theme_classic()
)
```

# Fitting models grouped by internet access with covariates
We now fit a new LGM with the participants grouped by whether or not they have access to a "good internet connection", and controlling for sex, birth year, ethnicity and mean household income.

```{r internet_covariates}
# Fitting no-change model
model_int_nc <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8

i ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_int_nc <- growth(model_int_nc, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Fitting linear model
model_int_lin <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_int_lin <- growth(model_int_lin, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing linear to no-change model
anova(fit_int_lin, fit_int_nc)

# Accepting linear over no-change model

# Fitting quadratic model
model_int_quad <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_int_quad <- growth(model_int_quad, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing quadratic to linear model
anova(fit_int_quad, fit_int_lin)

# Accepting quadratic over linear model

# Fitting model with error variances constrained to equality
model_int_con_ervar <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1, ervar1) * W9
CV4 ~~ c(ervar2, ervar2) * CV4
CV6 ~~ c(ervar3, ervar3) * CV6
CV8 ~~ c(ervar4, ervar4) * CV8

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_int_con_ervar <- growth(model_int_con_ervar, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing model with constrained error variances to free model
anova(fit_int_con_ervar, fit_int_quad)

# Accepting model with constrained error variances over free model

# Fitting model with constrained y-intercept
model_int_con_i <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1, ervar1) * W9
CV4 ~~ c(ervar2, ervar2) * CV4
CV6 ~~ c(ervar3, ervar3) * CV6
CV8 ~~ c(ervar4, ervar4) * CV8
 
i ~ c(i_1, i_1) * 1

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_int_con_i <- growth(model_int_con_i, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing model with constrained y-intercept to model without
anova(fit_int_con_i, fit_int_con_ervar)

# Accepting model with constrained y-intercept over model without

# Fitting model with constrained linear coefficient
model_int_con_i_s <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1, ervar1) * W9
CV4 ~~ c(ervar2, ervar2) * CV4
CV6 ~~ c(ervar3, ervar3) * CV6
CV8 ~~ c(ervar4, ervar4) * CV8
 
i ~ c(i_1, i_1) * 1
s ~ c(s_1, s_1) * 1

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_int_con_i_s <- growth(model_int_con_i_s, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing model with constrained linear coefficient to model without
anova(fit_int_con_i_s, fit_int_con_i)

# Rejecting model with constrained linear coefficient

# Fitting model with constrained quadratic coefficient
model_int_con_i_q <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1, ervar1) * W9
CV4 ~~ c(ervar2, ervar2) * CV4
CV6 ~~ c(ervar3, ervar3) * CV6
CV8 ~~ c(ervar4, ervar4) * CV8
 
i ~ c(i_1, i_1) * 1
q ~ c(q_1, q_1) * 1

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_int_con_i_q <- growth(model_int_con_i_q, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing model with constrained quadratic coefficient to model without
anova(fit_int_con_i_q, fit_int_con_i)

# Accepting model with constrained quadratic coefficient over model without
fit_int_prov <- fit_int_con_i_q

# Fitting model with constrained y-intercept variance
model_int_con_ivar <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1, ervar1) * W9
CV4 ~~ c(ervar2, ervar2) * CV4
CV6 ~~ c(ervar3, ervar3) * CV6
CV8 ~~ c(ervar4, ervar4) * CV8
 
i ~ c(i_1, i_1) * 1
q ~ c(q_1, q_1) * 1

i ~~ c(ivar, ivar) * i

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_int_con_ivar <- growth(model_int_con_ivar, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing model with constrained y-intercept variance to model without
anova(fit_int_con_ivar, fit_int_prov)

# Accepting model with constrained y-intercept variance over model without

# Fitting model with constrained linear coefficient variance
model_int_con_ivar_svar <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1, ervar1) * W9
CV4 ~~ c(ervar2, ervar2) * CV4
CV6 ~~ c(ervar3, ervar3) * CV6
CV8 ~~ c(ervar4, ervar4) * CV8
 
i ~ c(i_1, i_1) * 1
q ~ c(q_1, q_1) * 1

i ~~ c(ivar, ivar) * i
s ~~ c(svar, svar) * s

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_int_con_ivar_svar <- growth(model_int_con_ivar_svar, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing model with constrained linear coefficient variance to model without
anova(fit_int_con_ivar_svar, fit_int_con_ivar)

# Accepting model with constrained linear coefficient variance over model without

# Fitting model with constrained quadratic coefficient variance
model_int_con_ivar_svar_qvar <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1, ervar1) * W9
CV4 ~~ c(ervar2, ervar2) * CV4
CV6 ~~ c(ervar3, ervar3) * CV6
CV8 ~~ c(ervar4, ervar4) * CV8
 
i ~ c(i_1, i_1) * 1
q ~ c(q_1, q_1) * 1

i ~~ c(ivar, ivar) * i
s ~~ c(svar, svar) * s
q ~~ c(qvar, qvar) * q

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_int_con_ivar_svar_qvar <- growth(model_int_con_ivar_svar_qvar, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing model with constrained quadratic coefficient variance to model without
anova(fit_int_con_ivar_svar_qvar, fit_int_con_ivar_svar)

# Accepting model with constrained quadratic coefficient variance over model without
fit_int_prov <- fit_int_con_ivar_svar_qvar

# Fitting model with constrained y-intercept/linear coefficient covariance
model_int_con_iscovar <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1, ervar1) * W9
CV4 ~~ c(ervar2, ervar2) * CV4
CV6 ~~ c(ervar3, ervar3) * CV6
CV8 ~~ c(ervar4, ervar4) * CV8
 
i ~ c(i_1, i_1) * 1
q ~ c(q_1, q_1) * 1

i ~~ c(ivar, ivar) * i
s ~~ c(svar, svar) * s
q ~~ c(qvar, qvar) * q

i ~~ c(iscovar, iscovar) * s

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_int_con_iscovar <- growth(model_int_con_iscovar, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing model with constrained y-intercept/linear coefficient covariance to model without
anova(fit_int_con_iscovar, fit_int_prov)

# Accepting model with constrained y-intercept/linear coefficient covariance over model without

# Fitting model with constrained y-intercept/quadratic coefficient covariance
model_int_con_iscovar_iqcovar <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1, ervar1) * W9
CV4 ~~ c(ervar2, ervar2) * CV4
CV6 ~~ c(ervar3, ervar3) * CV6
CV8 ~~ c(ervar4, ervar4) * CV8
 
i ~ c(i_1, i_1) * 1
q ~ c(q_1, q_1) * 1

i ~~ c(ivar, ivar) * i
s ~~ c(svar, svar) * s
q ~~ c(qvar, qvar) * q

i ~~ c(iscovar, iscovar) * s
i ~~ c(iqcovar, iqcovar) * q

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_int_con_iscovar_iqcovar <- growth(model_int_con_iscovar_iqcovar, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing model with constrained y-intercept/quadratic coefficient covariance to model without
anova(fit_int_con_iscovar_iqcovar, fit_int_con_iscovar)

# Rejecting model with constrained y-intercept/quadratic coefficient covariance

# Fitting model with constrained linear coefficient/quadratic coefficient covariance
model_int_con_iscovar_sqcovar <- '
sex_merged ~ 1; sex_merged ~~ sex_merged
birthy ~ 1; birthy ~~ birthy
ethn_caucasian ~ 1; ethn_caucasian ~~ ethn_caucasian
mean_income ~ 1; mean_income ~~ mean_income

i =~ 1*W9 + 1*CV4 + 1*CV6 + 1*CV8
s =~ 0*W9 + 1*CV4 + 2*CV6 + 3*CV8
q =~ 0*W9 + 1*CV4 + 4*CV6 + 9*CV8

W9 ~~ c(ervar1, ervar1) * W9
CV4 ~~ c(ervar2, ervar2) * CV4
CV6 ~~ c(ervar3, ervar3) * CV6
CV8 ~~ c(ervar4, ervar4) * CV8

i ~ c(i_1, i_1) * 1
q ~ c(q_1, q_1) * 1

i ~~ c(ivar, ivar) * i
s ~~ c(svar, svar) * s
q ~~ c(qvar, qvar) * q

i ~~ c(iscovar, iscovar) * s
s ~~ c(sqcovar, sqcovar) * q

i ~ sex_merged + birthy + ethn_caucasian + mean_income
s ~ sex_merged + birthy + ethn_caucasian + mean_income
q ~ sex_merged + birthy + ethn_caucasian + mean_income
'

fit_int_con_iscovar_sqcovar <- growth(model_int_con_iscovar_sqcovar, data = data_sdq[!is.na(data_sdq$ypschlth2),], group = "ypschlth2", missing = "fiml", estimator = "mlr")

# Comparing model with constrained linear coefficient/quadratic coefficient covariance to model without
anova(fit_int_con_iscovar_sqcovar, fit_int_con_iscovar)

# Accepting model with constrained linear coefficient/quadratic coefficient covariance over model without
fit_int <- fit_int_con_iscovar_sqcovar

# Summary of unweighted model
summary(fit_int)

# Tabulating model output
semTable(fit_int, columns = c("estse", "p"), paramSets = c("latentmeans", "latentvariances", "latentcovariances", "residualvariances"), fits = c("chisq", "cfi", "rmsea"), varLabels = vlabs, file = "Data/Objects/sens_check_int_table.csv", type = "csv", print.results = FALSE)

# Saving model fit object
saveRDS(fit_int, file = "Data/Objects/sens_check_int.rds")

# Preparing LGM functions for plotting
pT <- parTable(fit_int)
fit_int_fn0 <- function(x) pT[pT$lhs == "i" & pT$op == "~1" & pT$group == 2,]$est + pT[pT$lhs == "s" & pT$op == "~1" & pT$group == 2,]$est*x + pT[pT$lhs == "q" & pT$op == "~1" & pT$group == 2,]$est*x^2
fit_int_fn1 <- function(x) pT[pT$lhs == "i" & pT$op == "~1" & pT$group == 1,]$est + pT[pT$lhs == "s" & pT$op == "~1" & pT$group == 1,]$est*x + pT[pT$lhs == "q" & pT$op == "~1" & pT$group == 1,]$est*x^2

# Using LGM parameters to predict individual trajectories
indiv_traj_p <- predict(fit_int)

# Extracting predicted individual trajectory data
indiv_traj0 <- data.frame(indiv_traj_p[["0"]])
indiv_traj1 <- data.frame(indiv_traj_p[["1"]])
i <- nrow(indiv_traj0)
j <- nrow(indiv_traj1)
```

### Final LGM (unweighted)

```{r internet_covariates_plot_1, echo = FALSE}
suppressMessages(
  ggplot() +
    annotate(geom = "rect", xmin = 5/6, xmax = 3.5, ymin = -Inf, ymax = Inf, fill = "grey", alpha = 0.3) +
    annotate(geom = "text", x = 3.45, y = 9, label = "COVID-19 pandemic", hjust = "right", vjust = "top") +
    geom_function(mapping = aes(colour = "No"), fun = fit_int_fn0, xlim = c(0, 3), size = 1) +
    geom_function(mapping = aes(colour = "Yes"), fun = fit_int_fn1, xlim = c(0, 3), size = 1) +
    scale_x_continuous(limits = c(0, 3.5), breaks = 0:3, labels = str_wrap(c("2017-19", "July 2020", "November 2020", "March 2021"), width = 10)) +
    ylim(9, 19) +
    xlab(NULL) +
    ylab("Total Difficulties score") +
    labs(colour = str_wrap("Has access to a good internet connection", width = 20)) +
    scale_colour_manual(values = c("No" = "#F8766D", "Yes" = "#00BFC4")) +
    theme_classic()
)
ggsave("Figures/int_sens.png")
ggsave("Figures/int_sens.svg")
```

### Final LGM (unweighted, by group with individual trajectories)

```{r internet_covariates_plot_2, echo = FALSE}
suppressMessages(
  ggplot() +
    annotate(geom = "rect", xmin = 5/6, xmax = 3.5, ymin = -Inf, ymax = Inf, fill = "grey", alpha = 0.3) +
    annotate(geom = "text", x = 3.45, y = 0, label = "COVID-19 pandemic", hjust = "right", vjust = "top") +
    lapply(1:i, function(i) geom_function(fun = function(x) indiv_traj0$i[i] + indiv_traj0$s[i] * x + indiv_traj0$q[i] * x^2, mapping = aes(colour = "No"), xlim = c(0, 3), size = 0.5, alpha = 20/nrow(indiv_traj0))) +
    geom_function(mapping = aes(colour = "No"), fun = fit_int_fn0, xlim = c(0, 3), size = 2) +
    scale_x_continuous(limits = c(0, 3.5), breaks = 0:3, labels = str_wrap(c("2017-19", "July 2020", "November 2020", "March 2021"), width = 10)) +
    xlab(NULL) +
    ylab("Total Difficulties score") +
    labs(colour = str_wrap("Has access to a good internet connection", width = 20), fill = NULL) +
    scale_colour_manual(values = c("No" = "#F8766D")) +
    theme_classic()
)

suppressMessages(
  ggplot() +
    annotate(geom = "rect", xmin = 5/6, xmax = 3.5, ymin = -Inf, ymax = Inf, fill = "grey", alpha = 0.3) +
    annotate(geom = "text", x = 3.45, y = 0, label = "COVID-19 pandemic", hjust = "right", vjust = "top") +
    lapply(1:j, function(j) geom_function(fun = function(x) indiv_traj1$i[j] + indiv_traj1$s[j] * x + indiv_traj1$q[j] * x^2, mapping = aes(colour = "Yes"), xlim = c(0, 3), size = 0.5, alpha = 20/nrow(indiv_traj1))) +
    geom_function(mapping = aes(colour = "Yes"), fun = fit_int_fn1, xlim = c(0, 3), size = 2) +
    scale_x_continuous(limits = c(0, 3.5), breaks = 0:3, labels = str_wrap(c("2017-19", "July 2020", "November 2020", "March 2021"), width = 10)) +
    xlab(NULL) +
    ylab("Total Difficulties score") +
    labs(colour = str_wrap("Has access to a good internet connection", width = 20), fill = NULL) +
    scale_colour_manual(values = c("Yes" = "#00BFC4")) +
    theme_classic()
)
```